Modal Abstractions for Virtualizing Memory Addresses

### 2025-07-23 examples_C.tex
a few more edits, but out of steam for the night

% The mapping operation of Figure \ref{fig:mapping_codeC} assumes an operation \textsf{walkpgdir} which must traverse the page tables
% in order to locate the address of the L1 entry to update --- 
% % possibly allocating tables for levels 3, 2, and 1 in the process,
% % installing them into levels 4, 3, and 2, along the way.
% possibly allocating new L3, L2, and L1 tables as necessary.

\todo[inline]{this and other figures need assertion updates to talk about C: see entry\_val (needs adjustment to points-to preconditions
and explanation of entry pointing to a C bitfield so entry\_val encompasses the various bits), nextpaddr
(was logical name in asm proof, but not a C variable)
}
\todo[inline]{need to narrate the main parts of assertions in prose}

@@

@@

  $\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus \{ \mathsf{entry} \}),m) \ast \textsf{entry} \mapsto_{\textsf{id}} \textsf{\_} \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$
  $\specline{ \textsf{entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{(pte\_initialized (entry\_val.pfn))} \urcorner }_{\rtv}$

@@

I would also expect to see a more prominent use of \textsf{v} in the precondition

@@

\todo[inline,color=cyan]{yes update logical entry to entryp, maybe remove entry $\mapsto$ v from $\Xi$ in first line?
and fix 20}

>>>>

@@

    $\specline{ \textsf{entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}}  \textsf{entry} \; \textsf{pte\_initialized(pfn\_set(entryv nextpaddr))} \ast \ulcorner  \textsf{qfrac} = 1 \land \lnot(\textsf{entry\_present entry\_val})  \urcorner }_{\rtv}$

@@

  $\specline{\textsf{P} \ast \mathcal{I}\texttt{ASpace}_{\textsf{id}}(\theta,\Xi\setminus \{ \mathsf{entry}\mapsto\textsf{v} \}),m) \ast \textsf{entry} \mapsto_{\textsf{id}} \textsf{\_} \ast \ghostmaptoken{\delta{}s}{\rtv}{\delta}  }_{\rtv}$
  $\specline{ \textsf{entry+KERNBASE} \mapsto_{\textsf{vpte,qfrac}} \textsf{entry} \; \textsf{(pte\_initialized (entry\_val.pfn))} \urcorner }_{\rtv}$

@@

@@

\todo[inline,color=cyan]{yes update logical entry to entryp, which requires also adding a local-variable assertion that entry the variable
holds entryp+KERNBASE}
